---
title: "Car Depreciation"
author: "Amy Fox"
date: "2/19/2020"
output: html_document
---


All data was retreived from https://usedfirst.com/cars/

Here are some brief descriptions of the columns:

- Year - The vehicle model year.
- New Price - The geometric mean new price paid of that model year grouped by most the popular trim levels.
- Current Price - The geometric mean listing price of a used model of that year grouped by the same trim levels.
- Maintenance - Estimated maintenance and repair costs during that year of ownership.
- $ Decline - Year over Year price decline.
- % Decline - Year over Year percentage of decline.
- % Paid - Percentage paid of the original price.
- % Left - Percentage left of reliable years of the vehicle.
- Years Left - Current industry average of years remaining with predictable maintenance and repair costs.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(readxl)
library(purrr)
library(dplyr)
library(tidyverse)
```

```{r}

car_files <- list.files("./Data/car_depreciation", full.names = TRUE)

car_filename <- data.frame(car_files)



mutate(file_contents = map(car_filename, ~read_xlsx(car_files)))

# this reads in all the files but I want to add a filename
map(car_files, read_xlsx) %>%
  reduce(rbind)


  mutate(file_contents = map(filename,          # read files into
           ~ read_csv(file.path(data_path, .))) # a new data column
        )

data <- files %>%
  # read in all the files, appending the path before the filename
  map(~ read_csv(file.path(data_path, .))) %>% 
  reduce(rbind)
```


```{r}
# try with mine

data_path <- "./Data/car_depreciation"   # path to the data
files <- dir(data_path, pattern = "*.xlsx") # get file names

level_key <- c(`honda-cr-v-depreciation.xlsx` = "Honda CRV",
               `hyundai-tucson-depreciation.xlsx`= "Hyundia Tucson",
               "mazda-cx-5-depreciation.xlsx" = "Mazda CX5",
               "nissan-rogue-depreciation.xlsx" = "Nissan Rogue",
               "toyota-rav4-depreciation.xlsx" = "Toyota Rav4")

car_data <- data_frame(filename = files) %>% # create a data frame with filenames
  mutate(file_contents = map(filename,          # read files into
           ~ read_xlsx(file.path(data_path, .))) # a new data column
        )  %>%
  unnest() %>%
  mutate(filename = recode(filename, !!!level_key)) %>%
  filter(!str_detect(Year, 'source'))


unique(car_data$Year)


ggplot(car_data, aes(x =factor(`Year`, levels = c(2019:2007)), y = `Current Price`, color = filename, 
                     group = filename)) +
  geom_point() +
  geom_path() +
  ggtitle("Car Price by Year") +
  xlab("Year") +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_y_continuous(breaks=c(5000, 10000, 15000, 20000, 25000, 30000))


ggplot(car_data, aes(x =factor(`Year`, levels = c(2019:2007)), y = `Percent Paid`, color = filename, 
                     group = filename)) +
  geom_point() +
  geom_path() +
  ggtitle("Depreciation of Vehicle") +
  xlab("Year") +
  theme(axis.text.x = element_text(angle = 90)) 
```

Based on the data it looks like it doesn't make sense to get a 2017 because the price is almost the same as a 2018.